---
title: "NFV test matrix"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(error = TRUE)
knitr::opts_chunk$set(fig.width = 10, fig.height = 8)
```

```{r warning=FALSE}
library(ggplot2)
library(dplyr)
```
```{r}
d <- read.csv("bench.csv")
d$id <- as.factor(d$id)
d$pktsize <- as.factor(d$pktsize)

overall <- subset(as.data.frame(d), subset = benchmark == 'iperf' | benchmark == 'l2fwd')

iperf <- droplevels(subset(overall, subset = benchmark == 'iperf'))
l2fwd <- droplevels(subset(overall, subset = benchmark == 'l2fwd'))

# data frames with NA scores (failures) replaced with 0
overall0 <- data.frame(overall)
overall0$score[is.na(overall$score)] <- 0

iperf0 <- data.frame(iperf)
iperf0$score[is.na(iperf0$score)] <- 0

l2fwd0 <- data.frame(l2fwd)
l2fwd0$score[is.na(l2fwd0$score)] <- 0

ggplot_distribution <- function(dataframe) {
  return (ggplot(dataframe, aes(x=score, y=..count..)) +
    theme(legend.position="top") +
    geom_histogram(aes(fill=snabb), position = "dodge", bins=20, alpha=0.5) +
    geom_density(aes(color=snabb)))
}


```

Performance comparison between Snabb versions. Compares scores with various benchmarks, workloads, configurations, and software dependency versions. Results are reported as [probability density graphs](https://en.wikipedia.org/wiki/Probability_density_function) showing the distribution of benchmark scores (measured in Gbps for iperf and Mpps for l2fwd).

The overall purpose of this report is to highlight the relative strengths and weaknesses between Snabb software versions. This is particularly intended for evaluating how experimental changes affect performance and reliability.

This report starts with a very broad summary and then drills down on iperf and l2fwd results separately.

## Overall summary

```{r fig.width=8, fig.height=4}
ggplot_distribution(overall0) + ggtitle("Overall")
```

### Split by benchmark

```{r fig.width=8, fig.height=6}
ggplot_distribution(overall0) + facet_wrap(~benchmark, scales = "free", ncol = 1, shrink = TRUE) + ggtitle("By benchmark")
```

## iperf

```{r fig.width=8, fig.height=4}
ggplot_distribution(iperf0) + ggtitle("iperf overall")
```

### Configuration

```{r}
ggplot_distribution(iperf0) +facet_wrap(~config, ncol=2, scales = "free_y", shrink = TRUE) + ggtitle("iperf by configuration")
```

### Guest kernel

```{r}
ggplot_distribution(iperf0) + facet_wrap(~kernel, ncol=2, scales = "free_y", shrink = TRUE) + ggtitle("iperf by guest kernel")
```

### QEMU

```{r}
ggplot_distribution(iperf0) + facet_wrap(~qemu, ncol=2, scales = "free_y", shrink = TRUE) + ggtitle("iperf by qemu")
```

### Success and failure

Success rate:

```{r}
success = summarize(group_by(iperf, qemu, kernel, config, snabb), success = mean(!is.na(score)))
ggplot(success, aes(qemu, config, fill=success)) +
  geom_tile(aes(fill=success)) + scale_fill_gradient(low="red", high="white") +
  geom_text(aes(label = scales::percent(success))) +
  facet_grid(snabb ~ kernel) +
  theme(axis.text.x = element_text(angle=45, vjust=1))
```

Sucesses:

```{r}
summary(subset(iperf, subset = !is.na(score), select = c(config, qemu, kernel)))
```

Failures:

```{r}
summary(subset(iperf, subset = is.na(score), select = c(config, qemu, kernel)))
```

## l2fwd

```{r fig.width=8, fig.height=4}
ggplot_distribution(l2fwd0) + ggtitle("l2fwd overall")
```

### Packet size

```{r fig.width=8, fig.height=6}
ggplot_distribution(l2fwd0) + facet_wrap(~pktsize, ncol=1) + ggtitle("l2fwd by packet size")
```

### Configuration

```{r}
ggplot_distribution(l2fwd0) + facet_wrap(~config, ncol=2, scales = "free_y", shrink = TRUE) + ggtitle("l2fwd by configuration")
```

### DPDK

```{r}
ggplot_distribution(l2fwd0) + facet_wrap(~dpdk, ncol=2, scales = "free_y", shrink = TRUE) + ggtitle("l2fwd by DPDK")
```

### DPDK + configuration

```{r}
ggplot_distribution(l2fwd0) + facet_wrap(dpdk ~ config, scales = "free_y", shrink = TRUE) + ggtitle("l2fwd by DPDK and configuration")
```

### QEMU

```{r}
ggplot_distribution(l2fwd0) + facet_wrap(~qemu, ncol=2, scales = "free_y", shrink = TRUE) + ggtitle("l2fwd by QEMU")
```

### Success and failure

Success rate:

```{r}
success = summarize(group_by(l2fwd, qemu, dpdk, config, snabb), success = mean(!is.na(score)))
ggplot(success, aes(qemu, dpdk, fill=success)) +
  geom_tile(aes(fill=success)) + scale_fill_gradient(low="red", high="white") +
  geom_text(aes(label = scales::percent(success))) +
  facet_grid(snabb ~ config) +
  theme(axis.text.x = element_text(angle=45, vjust=1))
```

Sucesses:

```{r}
summary(subset(l2fwd, subset = !is.na(score), select = c(config, qemu, dpdk, snabb, pktsize)))
```

Failures:

```{r}
summary(subset(l2fwd, subset = is.na(score), select = c(config, qemu, dpdk, snabb, pktsize)))
```
