---
title: "Vita benchmark report"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE, fig.width = 10, fig.height = 10)
```

```{r}
library(ggplot2)
results <- as.data.frame(read.csv("bench.csv"))
```

# vita-loopback

`vita-loopback` is a synthetic benchmark measuring Vita performance on a
single route with multiple packet sizes.

```{r}
# Select successful (score present) vita-loopback results
loopback = subset(results, subset=(benchmark == "vita-loopback" & score))
```

## Line graph

[Line graph](https://en.wikipedia.org/wiki/Line_graph) for a simple and direct
look at the results. The Y-scale starts at 0 to put the absolute differences in
perspective.

```{r}
p <- ggplot(loopback, aes(y=score, x=id, color=snabb))
p <- p + theme(legend.position="top")
p <- p + geom_point()
p <- p + geom_line()
p <- p + expand_limits(y=0)
p <- p + facet_grid(pktsize ~ benchmark, scales = "free")
p + ggtitle("Sequential test results")
```

## Box plot

[Box plot](https://en.wikipedia.org/wiki/Box_plot) to summarize the
distribution of results. The Y-axis origin is free to put focus on the relative
differences.

```{r}
p <- ggplot(loopback, aes(x=id, y=score, color=snabb))
p <- p + theme(legend.position="top")
p <- p + geom_boxplot(alpha=0.50)
p <- p + facet_grid(pktsize ~ benchmark, scales = "free")
p + ggtitle("Summary of test results")
```

## Density plot

[Density plot](https://en.wikipedia.org/wiki/Density_estimation) showing the
distribution of results. The curve is high around common values and low around
rare values. Here we can see how spread out they are, how they cluster
together, etc.

```{r}
p <- ggplot(loopback, aes(score, fill = snabb, color = snabb))
p <- p + theme(legend.position="top")
p <- p + geom_density(alpha = 0.1)
p <- p + facet_grid(pktsize ~ benchmark, scales = "free")
p + ggtitle("Shape (distribution) of test results")
```

## Cluster analysis

Cluster analysis using density-based spatial clustering of applications with
noise (DBSCAN).

```{r}
library(fpc)

cluster_label <- function (n) {
  if (n == 0) { NA } else { sprintf("c%s", n) }
}

print_ellipsis <- function (v, n) {
  print(v[1:min(length(v), n)])
  if (length(v) > n) { cat("...\n") }
}

plot_clusters <- function (conf) {
  eps <- sd(conf$score)/mean(conf$score) # eps := Coefficient of variation
  MinPts <- round(nrow(conf)/100)        # MinPts := 1% of total points

  conf$cluster <- dbscan(conf$score, eps=eps, MinPts=MinPts)$cluster

  # Ensure cluster labels are discrete
  conf$cluster <- sapply(conf$cluster, cluster_label)

  p <- ggplot(conf, aes(y=score, x=id, color=cluster))
  p <- p + theme(legend.position="top")
  p <- p + geom_point()
  p <- p + facet_grid(snabb ~ benchmark, scales = "free")
  print(p + ggtitle("Sequential test results colored by cluster"))

  cat("Cluster samples:\n")
  clusters <- unique(conf$cluster[!is.na(conf$cluster)])
  nSamples <- 10
  for (c in clusters) {
    cat(sprintf("%s: ", c))
    print_ellipsis(conf$id[!is.na(conf$cluster) & conf$cluster==c], nSamples)
  }
  cat("Outliers:\n")
  print_ellipsis(conf$id[is.na(conf$cluster)], nSamples)
}
```

### pktsize=IMIX

```{r}
plot_clusters(subset(loopback, subset=(pktsize=="IMIX")))
```

### pktsize=60

```{r}
plot_clusters(subset(loopback, subset=(pktsize=="60")))
```

### pktsize=600

```{r}
plot_clusters(subset(loopback, subset=(pktsize=="600")))
```

### pktsize=1000

```{r}
plot_clusters(subset(loopback, subset=(pktsize=="1000")))
```


## Tukey test

Differences between Vita versions.

```{r}
TukeyHSD(aov(score ~ snabb, data=loopback))
```
